\singlespacing \vspace{-1.5cm} \LARGE Trade-offs among plant reproductive traits determine interactions with floral visitors

### 2021-10-06 Manuscript/Manuscript.Rmd
edits

>>>>

# Acknowledgements

We thank all researchers that made their data available for our analysis. We thank Bryony Wilcox, Greg Bible, Mercedes Sanchez-Lanuza and David Ragel for their help with data collection. We also thank Jason Tylianakis for his comments on the manuscript before submission. JBL thanks the University of New England for the funding provided to carry out this work.

### 2021-10-06 Manuscript/Manuscript.tex
edits

>>>>

\section{Acknowledgements}\label{acknowledgements}

We thank all researchers that made their data available for our
analysis. We thank Bryony Wilcox, Greg Bible, Mercedes Sanchez-Lanuza
and David Ragel for their help with data collection. We also thank Jason
Tylianakis for his comments on the manuscript before submission. JBL
thanks the University of New England for the funding provided to carry
out this work.
